Unit tests

### 2018-04-24 Tests.Rmd
Tests for Cause4copula.R added

# Tests for retd() function from ExtremeTailDep.R
<!--DCR to add this section-->

@@

>>>>

# Tests for retd() function from ExtremeTailDep.R

DCR to add this section

@@

# Tests for Cause4copula.R

**Test for `GetNoise` function**

```{r test_GetNoise, echo=T}
set.seed(seed=101)
source("Cause4copula.R")
# Here we generate noise with 5000 points drawn from Clayton copula with Kendall's tau=0.5 
s<-GetNoise(N=5000,fcode=3,corcoef=0.5,method="kendall",ploton=T) # plot in copula space
s1<-s$noise_q
hist(s1[,1],breaks=1000) # This should be normal distribution
hist(s1[,2],breaks=1000) # This should be normal distribution
plot(s1[,1],s1[,2],col="red") # plot after qnorm

# Here we also checked C or SC copula 
# with same spearman's rho/ kendall's tau have same parameter
tgcop<-claytonCopula(3,2)
tgcop2<-rotCopula(tgcop)
iRho(tgcop,0.5)==iRho(tgcop2,0.5) # check if it is True?
iTau(tgcop,0.5)==iTau(tgcop2,0.5) # check if it is True?
```

**Test for `Simulator_Cause4copula` and `comp` function**

```{r test_Simulator_Cause4copula, echo=T}
set.seed(seed=101)
source("Cause4copula.R")
# when noise comes from a clayton cop with spearmancor=0.8
s<-GetNoise(N=5000,fcode=3,corcoef=0.8,method="spearman",ploton=T) # noise copula
s2<-Simulator_Cause4copula(cons=0.5,p0=c(0,0),noise=s$noise_q)
points(s2$pop_c[,1],s2$pop_c[,2],col="green") # population copula
hist(s2$pop_q[,1],breaks=1000) # check if it's normal
hist(s2$pop_c[,1],breaks=1000) # check if it's uniform
num_keep_last<-500
zz<-comp(s=s,s2=s2,num_keep_last=num_keep_last)
zz$comp
x<-c(dim(zz$last_num_keep_noise$last_num_keep_noise_c)[1],
     dim(zz$last_num_keep_noise$last_num_keep_noise_q)[1],
     dim(zz$last_num_keep_pop$last_num_keep_pop_c)[1],
     dim(zz$last_num_keep_pop$last_num_keep_pop_c)[1])
if(all(x==num_keep_last)){
  print("passed")
}else{
  print("failed")
}
```
